Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-06 Manuscript/manuscript.tex
Small updates -- mostly todos.

@@

@@

The difference between the affinities of \ce{Na^+} and \ce{K^+} to neutral and negatively charged membranes
can be described by their relative surface excesses with respect to water, $\Gamma ^{w} _{ion}$, 
which are shown in the plots of the density profiles of the ions in Figs.~\ref{fig:nacl-dens} (neutral bilayer) and \ref{fig:nacl-dens_PCPS} (negatively charged bilayer). 
Such a quantity compares the adsorption of ions to the adsorption of water molecules at an interface 
without the necessity of defining a Gibbs dividing surface. \citep{melcr18, chattorajBOOK}
While \ce{K^+} maintains negative values of $\Gamma^{w}_{K}$ even for the negatively charged bilayer,
the value of $\Gamma^{w}_{Na}$ for \ce{Na^+} changes from negative to positive
in a neutral POPC bilayer versus in a negatively charged bilayer with the composition 5\,PC:1\,PS.
%This means that at the given concentration the bilayer interface has a small preference to \ce{Na^+} cations compared to water molecules. 
Interestingly, this value is slightly decreased in the presence of an additional \ce{NaCl} concentration adding also \ce{Cl^-} anions, 
which are not present in the system when only counterions are used
(bottom resp. top plot in Fig.~\ref{fig:nacl-dens_PCPS}). 
The interaction of a neutral POPC bilayer with \ce{NaCl} is discussed in a greater detail in our publication \citep{melcr18}.

@@

\begin{figure}[htbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/density_profiles_ca_na_cl_wat_phos_models-compar_1-3_CaCl2-series.pdf}
  \caption{\label{fig:cacl-dens_PCPS} 
    Number density profiles of \ce{Ca^{2+}}, \ce{Na^{+}} and \ce{Cl^-} along the normal of the membrane starting at the centre
    for the negatively charged membrane with the composition 5\,PC:1\,PS
    at various bulk concentrations of \ce{CaCl2} from simulations with ECC-lipids. 
    All profiles contain \ce{Na^+} counterions and an additional concentration of \ce{CaCl2}. 
    In order to visualize the density profiles with a scale comparable to the profile of \ce{Ca^{2+}},  
    the density profiles of~\ce{Cl^-} ions are divided by 2, and 
    the density profiles of phosphate groups and water are divided by 5 and 200, respectively.  
    } 
\todo{JM: Compare with pure POPC bilayer? 
SAMULI: Comparison of the relative surface excess values in the text and in the table would be probably sufficient.}
\end{figure}

@@

\subsection{Electronic Continuum Correction as a generally applicable model polarizability?}

\textbf{This will be exemplified on POPS throughout this paper and, hence, it does not require additional section. }

\todo{Look up possible applications of AMOEBA and Drude on anions/cations and possibly lipids. 
Does ECC provide improvment over them? 
This is crucial -- if this section will make the core message of this paper, 
I have to put the ECC-method into context of other polarizable models. 
If there are no other simulations like these and no data on the accuracy with cation/anions, 
our approach (ECC) is hence the pioneer in the field and, hence, sets the standard instead. 
SAMULI: We should keep the focus on lipids here. We should check the recent literature, but
I am not aware of charged lipid simulations with explicitly polarizable force fields. 
As for PC, the charge scaling was used in the early simulations of PS lipids from Berendsen group.
We should mention this. Otherwise, I think that one of our conclusions will be that our
results indicate that ECC generally improves the results of lipids bilayer MD simulations.
However, we should not write a separate section about it. It should be in the conclusions section.}

Show the successes and possible \emph{limits} of ECC applied on top of various models \cite{melcr18, martinek17, Pluharova2014, kohagen14, kohagen16}.

After validation above, it can be an option to show results also for systems, for which we have no experiments.

>>>>

\todo{ Make a literature search for any possible applications of polarizable force fields (AMOEBA and Drude) on anions/cations and lipids. 
If found -- Does ECC provide improvment over them? 
As for PC, the charge scaling was used in the early simulations of PS lipids from Berendsen group.  }

@@

\todo{Joe: It might be a very short section -- Shall we merge it with the simulation details section?}

@@

The difference between the affinities of \ce{Na^+} and \ce{K^+} to neutral and negatively charged membranes
can be described by their relative surface excesses with respect to water, $\Gamma ^{w} _{ion}$, 
which are shown in the plots of the density profiles of the ions in Figs.~\ref{fig:nacl-dens} (neutral bilayer) and \ref{fig:nacl-dens_PCPS} (negatively charged bilayer). 
Such a quantity compares the adsorption of ions to the adsorption of water molecules at an interface 
without the necessity of defining a Gibbs dividing surface. \citep{melcr18, chattorajBOOK}
While \ce{K^+} maintains negative values of $\Gamma^{w}_{K}$ even for the negatively charged bilayer,
the value of $\Gamma^{w}_{Na}$ for \ce{Na^+} changes from negative to positive
in a neutral POPC bilayer versus in a negatively charged bilayer with the composition 5\,PC:1\,PS.
%This means that at the given concentration the bilayer interface has a small preference to \ce{Na^+} cations compared to water molecules. 
Interestingly, this value is slightly decreased in the presence of an additional \ce{NaCl} concentration adding also \ce{Cl^-} anions, 
which are not present in the system when only counterions are used
(bottom resp. top plot in Fig.~\ref{fig:nacl-dens_PCPS}). 
The relative surface excess of calcium, $\Gamma^{w}_{Ca}$, also reflects
the higher affinity of the negatively charged PC:PS (5:1) membrane compared to a neutral POPC bilayer; 
its value for the latter is       $\Gamma^{w}_{Ca} = 0.06\mathrm{nm^{-2}}$, 
while for the PC:PS mixture it is $\Gamma^{w}_{Ca} = 0.24\mathrm{nm^{-2}}$
at comparable concentrations $C _{Ca} = 260\pm 30 \mathrm{mM} $.

@@

\begin{figure}[htbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/density_profiles_ca_na_cl_wat_phos_models-compar_1-3_CaCl2-series.pdf}
  \caption{\label{fig:cacl-dens_PCPS} 
    Number density profiles of \ce{Ca^{2+}}, \ce{Na^{+}} and \ce{Cl^-} along the normal of the membrane starting at the centre
    for the negatively charged membrane with the composition 5\,PC:1\,PS
    at various bulk concentrations of \ce{CaCl2} from simulations with ECC-lipids. 
    All profiles contain \ce{Na^+} counterions and an additional concentration of \ce{CaCl2}. 
    In order to visualize the density profiles with a scale comparable to the profile of \ce{Ca^{2+}},  
    the density profiles of~\ce{Cl^-} ions are divided by 2, and 
    the density profiles of phosphate groups and water are divided by 5 and 200, respectively.  
    } 
\end{figure}

@@
